---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(tidymodels)
library(janitor)
library(gridExtra)
library(fabletools)
library(pins)
library(RODBC)

options(scipen = 999)
theme_set(theme_minimal())

'%notin%' <- Negate(`%in%`)

board <- board_folder(getwd())
train <- board %>% pin_read('hc_train')

db <- odbcDriverConnect('DRIVER={SQL SERVER};SERVER=LAPTOP-LT2BSKO0\\SQLEXPRESS;DATABASE=HOME_CREDIT')
```








# Missing values
```{r}
colSums(is.na(train))[colSums(is.na(train)) > 0]
```

```{r}
train %>% select_if(negate(is.numeric)) %>% str()
```

# Automated EDA Function for simple exploration
```{r}
# - auto eda ---------------------------------------------
auto_eda <-
  tryCatch(
      function(df, vars, target){
        
    base_default_rate <- 
      df %>% 
      summarize(mean(!!as.symbol(target))) %>% 
      pull()
    
    df <-
      df %>% 
      mutate_at(c(target), as.character) %>% 
      mutate_at(c(target), as.numeric)
    
    
    for(x in vars){
     if (nrow(data.frame(unique(df[, x]))) >= 20 & is.numeric(df[, x])){
       
       minval <- min(df[, x]) - 1
       maxval <- max(df[, x]) + 1
       quantiles <- unique(c(minval, quantile(df[, x], seq(0, 1, .1), na.rm = TRUE), maxval))
       
       tstep <-
         df %>% 
         mutate({{x}} := fct_explicit_na(cut(!!as.symbol(x), breaks = quantiles))) %>% 
         group_by(.dots = x) %>% 
         summarize(default_rate = mean(!!as.symbol(target)),
                   cnt = n())
         
     } else{
       
       tstep <-
         df %>% 
         group_by(.dots = x) %>% 
         summarize(default_rate = mean(target),
                   cnt = n())
     }
      
       p1 <-
         tstep %>% 
         ggplot(aes(x = fct_rev(factor(!!as.symbol(x))), y = cnt)) +
         geom_bar(stat = 'identity', width = .6, fill = '#53868b') +
         labs(title = x, x = NULL, y = 'Count') +
         coord_flip() +
         theme_light() 
       
       
       p2 <-
         tstep %>% 
         ggplot(aes(x = fct_rev(factor(!!as.symbol(x))), y = default_rate)) +
         geom_bar(stat = 'identity', width = .5, fill = '#53868b') +
         labs(title = x, x = NULL, y = 'Default Rate') +
         coord_flip() +
         theme_light() +
         geom_hline(yintercept = base_default_rate, color = 'indianred', linetype = 'dashed')
       
       plot <- grid.arrange(p1, p2, nrow = 2)
       plot
      
    }
  },
  error = function(e){
    print(x)
  }
    
  )


# - facet wrap eda ---------------------------------------------
eda_facet_wrap <-
  function(df, vars, target, facet_var){
    # takes a categorical variable (facet_var) with a numerical variable
    base_default_rate <- 
      df %>% 
      summarize(mean(!!as.symbol(target))) %>% 
      pull()
    
    df <-
      df %>% 
      mutate_at(c(target), as.character) %>% 
      mutate_at(c(target), as.numeric)
    
    for (x in vars){
     if (nrow(data.frame(unique(df[, x]))) >= 20 & is.numeric(df[, x])){
       
       minval <- min(df[, x]) - 1
       maxval <- max(df[, x]) + 1
       quantiles <- unique(c(minval, quantile(df[, x], seq(0, 1, .1), na.rm = TRUE), maxval))
       
        tstep <-
         df %>% 
         mutate({{x}} := fct_explicit_na(cut(!!as.symbol(x), breaks = quantiles))) %>% 
         group_by(.dots = x, !!as.symbol(facet_var)) %>% 
         summarize(default_rate = mean(!!as.symbol(target)),
                   cnt = n()) 
     }
      
      p <- 
        tstep %>% 
        ggplot(aes(x = fct_rev(factor(!!as.symbol(x))), y = default_rate)) +
        geom_bar(stat = 'identity', width = .5, fill = '#53868b') +
        geom_hline(yintercept = base_default_rate, color = 'indianred', linetype = 'dashed') +
        facet_wrap(as.formula(paste("~", facet_var))) +
        labs(title = x, x = NULL, y = 'Default Rate') +
        coord_flip() +
        theme_light()
    
      grid.arrange(p)
    
    }
  }

```


# Application Data

Start off analyzing data where very little is missing. 
```{r, warning=FALSE, message=FALSE, fig.height=7, fig.width=7}

base_df_rate = mean(as.numeric(as.character(train$target)))
train_vars <- names(colSums(is.na(train))[colSums(is.na(train)) < 1000])

train %>% 
  auto_eda(vars =  train_vars,
           target =  'target', 
           base_default_rate = base_df_rate)
```

# Bureau Data
```{r}
bb <-
  sqlQuery(
    db,
    "
        SELECT
        B.*

        FROM dbo.APPLICATION_DATA A
        	LEFT JOIN dbo.HC_BUREAU B
        		on A.SK_ID_CURR = B.SK_ID_CURR
        WHERE DATA_SPLIT = 'TRAIN'
           "
  ) %>%
  clean_names()

bb <-
  train %>% 
    select(sk_id_curr, target) %>% 
    inner_join(bb, by = 'sk_id_curr')
```

```{r}
bb_vars <-
  bb %>% 
  select(-sk_id_curr, -sk_id_bureau) %>% 
  names()

bb %>% 
  auto_eda(vars = bb_vars, target = 'target')
```


days_credit: the longer the credit has been open, the less likely the account is to default. 
credit_day_overdue: if the account has overdue days, it's more likely to default.
days_credit_enddate: what does this mean? Higher values more likely to default
days_enddate_fact: related to closed accounts (most likely number of days since close?). If an account closed recently, more likely to default.
amt_credit_max_overdue: higher values more likely to default. 
amt_credit_sum: this
amt_credit_sum_debt: having debt more likely to default.
days_credit_update: how many days before application did last credit information come, the higher the value the more likely to default.
amt_annuity: having annuity values leads to higher default rate.


```{r}
bb %>% 
  filter(credit_active != 'Bad debt') %>% 
  eda_facet_wrap(vars = c('days_credit', 'days_credit_enddate', 'days_enddate_fact', 'amt_credit_max_overdue', 
                          'amt_credit_sum', 'amt_credit_sum_debt', 'days_credit_update'),
                target = 'target', facet_var = 'credit_active')
```










ideas:
* what is the total amount of credit compared to their credit limit?
* compare credit length to age
* Look at credit types and the amounts associated with them. You might even be able to create a simple model to gain some understanding of these. 

# Bureau Balance
Monthly balances of previous credits in Credit Bureau.

```{r}
bal <-
  sqlQuery(
    db,
    "
        SELECT
        B.*

        FROM dbo.APPLICATION_DATA A
        	LEFT JOIN dbo.HC_BUREAU_BALANCE B
        		on A.SK_ID_CURR = B.SK_ID_CURR
        WHERE DATA_SPLIT = 'TRAIN'
           "
  ) %>%
  clean_names()

bal <-
  train %>% 
    select(sk_id_curr, target) %>% 
    inner_join(bal, by = 'sk_id_curr')

head(bal)
```


# Credit Card Balance
Monthly balance of client's previous credit card loans in Home Credit

```{r}
cb <-
  sqlQuery(
    db,
    "
        SELECT
        B.*

        FROM dbo.APPLICATION_DATA A
        	LEFT JOIN dbo.HC_CREDIT_CARD_BALANCE B
        		on A.SK_ID_CURR = B.SK_ID_CURR
        WHERE DATA_SPLIT = 'TRAIN'
           "
  ) %>%
  clean_names()

cb <-
  train %>% 
    select(sk_id_curr, target) %>% 
    inner_join(cb, by = 'sk_id_curr')
```

```{r}
head(cb)
```


### amt_credit_sum
```{r}
bb %>% 
  group_by(sk_id_curr, target) %>% 
  summarize(amt_credit_sum = sum(amt_credit_sum)) %>% 
  auto_eda(vars = c('amt_credit_sum'), target = 'target',base_default_rate =  base_df_rate)
```







