---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(tidymodels)
library(pins)
library(bonsai)
library(lightgbm)
library(doParallel)
library(vip)

board <- board_folder(getwd())
```

```{r}
train <- 
  board %>% 
  pin_read('hc_train') %>% 
  mutate(target = as.factor(target))

head(train)
```

```{r}
set.seed(42)
folds <- vfold_cv(train, v = 5)
```


# Build Recipie
```{r}

lgbm_r1 <-
    recipe(target ~
           name_contract_type +
           code_gender + 
           flag_own_car +
           cnt_children + 
           cnt_fam_members +
           amt_income_total +
           amt_credit +
           amt_annuity +
           name_education_type +
           name_family_status +
           days_birth +
           days_employed +
           region_rating_client +
           ext_source_2 +
           amt_income_total 
         , data = train
           ) %>% 
  step_mutate(age = days_birth / -365,
              credit_to_income = amt_income_total / amt_credit,
              cnt_adults = cnt_fam_members - cnt_children,
              income_per_family_member = amt_income_total / cnt_fam_members) %>% 
  step_rm(days_birth) 



lgbm_r2 <-
    recipe(target ~
           name_contract_type +
           code_gender + 
           flag_own_car +
           flag_own_realty +
           cnt_children + 
           amt_income_total +
           amt_credit +
           amt_annuity +
           amt_goods_price +   
           name_income_type + 
           name_education_type +
           name_family_status +
           name_housing_type +
           region_population_relative +
           days_birth +
           days_employed +
           days_registration +
           days_id_publish +
           flag_emp_phone +
           flag_work_phone +
           flag_phone +
           cnt_fam_members +
           region_rating_client +
           region_rating_client_w_city +
           hour_appr_process_start +
           reg_city_not_live_city +
           reg_city_not_work_city +
           live_city_not_work_city +
           ext_source_2 +
           def_30_cnt_social_circle +
           def_60_cnt_social_circle + 
           obs_60_cnt_social_circle +
           days_last_phone_change +
           flag_document_3 +
           flag_document_6 +
           flag_document_8 
         , data = train
           ) %>% 
  step_mutate(single_parent = ifelse(cnt_fam_members - cnt_children == 1 & cnt_children > 0, 1, 0),
              income_per_fam_member = round(amt_income_total / cnt_fam_members, 0)/1000,
              perc_sc_default_60 = def_60_cnt_social_circle / obs_60_cnt_social_circle,
              perc_sc_default_60 = replace(perc_sc_default_60, is.na(perc_sc_default_60), 0),
              credit_to_income = amt_income_total / amt_credit,
              income_per_goods_price = amt_income_total / amt_goods_price,
              amt_credit_goods_price_diff = amt_credit - amt_goods_price)


lgbm_r3 <-
    recipe(target ~
           name_contract_type +
           code_gender + 
           flag_own_car +
           flag_own_realty +
           cnt_children + 
           amt_income_total +
           amt_credit +
           amt_annuity +
           amt_goods_price +   
           name_income_type + 
           name_education_type +
           name_family_status +
           name_housing_type +
           region_population_relative +
           days_birth +
           days_employed +
           days_registration +
           days_id_publish +
           flag_emp_phone +
           flag_work_phone +
           flag_phone +
           cnt_fam_members +
           region_rating_client +
           region_rating_client_w_city +
           hour_appr_process_start +
           reg_city_not_live_city +
           reg_city_not_work_city +
           live_city_not_work_city +
           ext_source_2 +
           def_30_cnt_social_circle +
           def_60_cnt_social_circle + 
           obs_60_cnt_social_circle +
           days_last_phone_change +
           flag_document_3 +
           flag_document_6 +
           flag_document_8 +
           ext_source_1 +
           ext_source_3 +
           own_car_age +
           occupation_type +
           floorsmax_avg +
           emergencystate_mode +
           amt_req_credit_bureau_year
         , data = train
           ) %>% 
  step_mutate(single_parent = ifelse(cnt_fam_members - cnt_children == 1 & cnt_children > 0, 1, 0),
              income_per_fam_member = round(amt_income_total / cnt_fam_members, 0)/1000,
              perc_sc_default_60 = def_60_cnt_social_circle / obs_60_cnt_social_circle,
              perc_sc_default_60 = replace(perc_sc_default_60, is.na(perc_sc_default_60), 0),
              credit_to_income = amt_income_total / amt_credit,
              income_per_goods_price = amt_income_total / amt_goods_price,
              amt_credit_goods_price_diff = amt_credit - amt_goods_price)

juice(prep(lgbm_r3)) %>% select(-target)


lgbm_r4 <- 
  recipe(
    target ~ .,
  data = train) %>% 
    step_mutate(single_parent = ifelse(cnt_fam_members - cnt_children == 1 & cnt_children > 0, 1, 0),
              income_per_fam_member = round(amt_income_total / cnt_fam_members, 0)/1000,
              perc_sc_default_60 = def_60_cnt_social_circle / obs_60_cnt_social_circle,
              perc_sc_default_60 = replace(perc_sc_default_60, is.na(perc_sc_default_60), 0),
              credit_to_income = amt_income_total / amt_credit,
              income_per_goods_price = amt_income_total / amt_goods_price,
              amt_credit_goods_price_diff = amt_credit - amt_goods_price)

juice(prep(lgbm_r4)) %>% select(-target)

```
```{r}
get_cv_lgbm <-
  function(recipe, iterations, no_improve){
    
    set.seed(42)
    
    model <-
      boost_tree(
        trees = tune(),
        mtry = tune(),
        min_n = tune(),
        tree_depth = tune(),
        learn_rate = tune(),
        loss_reduction = tune()
      ) %>% 
      set_engine('lightgbm') %>% 
      set_mode('classification')
    
    wf <-
      workflow() %>% 
      add_model(model) %>% 
      add_recipe(recipe)
    
    params <-
      wf %>% 
      extract_parameter_set_dials() %>% 
      finalize(juice(prep(recipe)) %>% select(-target))
    
    cl <- makePSOCKcluster(detectCores() - 2)
    registerDoParallel(cl)
    
    search <-
      wf %>% 
      tune_bayes(
        resamples = folds,
        param_info = params,
        iter = iterations,
        control = control_bayes(save_pred = TRUE, save_workflow = TRUE, verbose = TRUE, no_improve = no_improve),
        metrics = metric_set(roc_auc)
      )
    
    stopCluster(cl)
    
    # save predictions to be used for future access
    preds <-
      search %>% 
      collect_predictions() %>% 
      filter(
        .config == search %>% select_best('roc_auc') %>% select(.config) %>% pull()
      )
    
    # create a dataframe that can be used for generating model performance metrics
    perf_df <-
      preds %>% 
      rename(pred = .pred_1, truth = target) %>% 
      mutate(pred_class = as.factor(ifelse(pred >= mean(as.numeric(as.character(train$target))), 1, 0))) %>% 
      select(pred, pred_class, truth)
    
    return(list(workflow = wf, search = search, predictions = preds, performance_df = perf_df))
      
    
    
  }
```

```{r}
perf_r1 <- get_cv_lgbm(recipe = lgbm_r1) #roc_auc=0.7075
perf_r2 <- get_cv_lgbm(recipe = lgbm_r2) #roc_auc=0.7236
perf_r3 <- get_cv_lgbm(recipe = lgbm_r3, iterations = 50, no_improve = 20) #.758
perf_r4 <- get_cv_lgbm(recipe = lgbm_r4, iterations = 50, no_improve = 20)

```
# ROC
```{r}
perf_r3$search %>% show_best()
```
# Recall - True Positive Rate - the proportion of true positives identified by the model (TP / (TP + FN))
```{r}
yardstick::recall(perf_r3$performance_df, truth = truth, estimate = pred_class, event_level = 'second')
```


# Precision - The proportion of true positives among examples predicted as positive: among all of the positive predictions, what proportion were correct? (TP / (TP + FP))
```{r}
yardstick::precision(perf_r3$performance_df, truth = truth, estimate = pred_class, event_level = 'second')
```


# Confusion Matrix
```{r}
get_conf_matrix <-
  function(perf_object){
    conf_matrix <-
      perf_object %>% 
      conf_mat(truth = truth, estimate = pred_class)
    
    conf_matrix %>% 
      tidy() %>% 
      inner_join(
        data.frame(join = 'join', cell_1_1 = 'TN', cell_2_1 = 'FP', cell_1_2 = 'FN', cell_2_2 = 'TP') %>% 
          pivot_longer(-join, values_to = 'label') %>% 
          select(name, label)) %>% 
      mutate(perc = value / nrow(train))
  }
```




```{r}
get_conf_matrix(perf_r3$performance_df)
```



# ROC Curve
```{r}
get_auc_roc <-
  function(predictions, type = 'auc'){
    cv_preds <-
      predictions %>% 
      arrange(.row) %>% 
      select(.pred_1, .row, target) %>% 
      rename(prob = .pred_1)
    
    if(type == 'auc'){
      return(roc_auc(cv_preds, truth = target, prob, event_level = 'second') %>% select(.estimate) %>% pull())
    }
    else if(type == 'roc'){
      return(roc_curve(cv_preds, truth = target, prob, event_level = 'second'))
      }
    }
  
```

```{r}
auc_r1 <- get_auc_roc(perf_r1$predictions, 'auc')
roc_r1 <- get_auc_roc(perf_r1$predictions, 'roc')

auc_r2 <- get_auc_roc(perf_r2$predictions, 'auc')
roc_r2 <- get_auc_roc(perf_r2$predictions, 'roc')


ggplot() +
  geom_line(data = roc_r2, aes(x = 1 - specificity, y = sensitivity, color = paste('R1', formattable::percent(auc_r2)))) +
  labs(color = NULL)

```

# Finalize workflow
```{r}

finalized_r1 <-
  perf_r1$workflow %>% 
  finalize_workflow(perf_r1$search %>% select_best('roc_auc')) %>% 
  fit(train)
```

```{r}
predict_function_gbm <-  function(model, newdata) {
    predict(model, newdata) %>% pluck(.,1)
}
```


```{r}
fastshap::explain(
  finalized_r1,
  X = as.data.frame(juice(prep(lgbm_r1)) %>% select(-target)),
  pred_wrapper = predict_function_gbm,
  nsim = 10
)
```


```{r}
finalized_r1 %>% 
  pull_workflow_fit() %>% 
  vip(geom = 'point')
```


# Error Analysis

Recipe 2 has a high false positive rate, predicting those who don't default as likely to default. This is a costly mistake as it prevents potentially good borrowers from receiving a loan, thereby decreasing profits. We need to focus efforts on decreasing the false positive rate by identifying features that help identify negative instances.

```{r}
perf_r2$
```



